The Evolution of Phenotypically Invariant Genetic Networks

### 2017-12-06 kalman_walk_paper.tex
de-emphed hybrid breakdown in discussion

Consistent with empirical observation of \emph{hybrid breakdown} \citep[e.g.][]{plotner2017chlorosis}, 
we see that the fitnesses of $F_2$ hybrids drop at a much faster rate than those of $F_1$s.
% since $F_1$ and $F_2$ phenotypes diverge linearly and at the square root of time relative to parentals, respectively.
%\plr{refer to Turelli here}
% In this model, this is due to recombination shuffling system architectures, leaving the $F_2$ system homozygous for one parent at one particular locus and homozygous for the other parent at another possibly incompatible locus.
Another natural consequence of the model is Haldane's rule,
that if only one $F_1$ hybrid sex is inviable or sterile it is likely to be the heterogametic sex.
This occurs because if the genes underlying a regulatory network are distributed among both autosomes and the sex chromosome, 
then heterogametic $F_1$s show variation similar to that seen in $F_2$s.

>>>>

Consistent with empirical observation of hybrid breakdown \citep[e.g.][]{plotner2017chlorosis}, 
we see that the fitnesses of $F_2$ hybrids drop at a much faster rate than those of $F_1$s.
% since $F_1$ and $F_2$ phenotypes diverge linearly and at the square root of time relative to parentals, respectively.
%\plr{refer to Turelli here}
% In this model, this is due to recombination shuffling system architectures, leaving the $F_2$ system homozygous for one parent at one particular locus and homozygous for the other parent at another possibly incompatible locus.
Another natural consequence of the model is Haldane's rule,
that if only one $F_1$ hybrid sex is inviable or sterile it is likely to be the heterogametic sex.
This occurs because if the genes underlying a regulatory network are distributed among both autosomes and the sex chromosome, 
then heterogametic $F_1$s show variation similar to that seen in $F_2$s.
